---
title: "Flexible Regression Outputs with `{fixest}`"
date: "March 1, 2025"
# lastmod: "November 30, 2024"
toc: true
toc-expand: true
toc-title: "Table of Contents"
number-sections: true

header-includes: |
    <style>
    h1.title {
      text-align: center;
      margin-top: 15px;
    }
    h2 {
      margin-top: 60px;
    }
    h3 {
      margin-top: 20px;
    }
    </style>
---

\

## Overview

- Still under construction.
- This note demonstrates flexible regression analyses and table outputs with the `{fixest}` package.
- `{fixest}` is a fast and flexible package for estimating fixed-effects models.
- Main reference: [stata2R---fixest](https://stata2r.github.io/fixest/).  


## Setup

### Package

```{r}
pacman::p_load(tidyverse, fixest)
```

### Read data

```{r}
df <- readr::read_csv("https://raw.githubusercontent.com/stata2r/stata2r.github.io/main/data/cps_long.csv")

df |> glimpse()
```


## Set Dataset Grobally

- Set the dataset globally using `setFixest_estimation()` function so that we don't need to specify the data argument in the `feols()` function in each estimation.
- In Section 3, we will speficy the data argument in the `feols()` function to show how it works.
- In Section 4 onward, we won't specify the data argument in the `feols()` function.

```{r}
fixest::setFixest_estimation(data = df)
```


## Basic Estimation with `feols()`

### Multiple variables

```{r}
df |> feols(
  wage ~ educ + age + black + marr
)
```

- Note: `etable()` function is used to display the estimation results in a nice table format.

```{r}
df |> feols(
  wage ~ educ + age + black + marr
) |> 
  etable()
```

### Multiple fixed effects

```{r}
df |> feols(
  wage ~ educ + age + black + marr | 
    countyfips + year
)
```

### Clustered standard errors with `vcov`

```{r}
df |> feols(
  wage ~ educ + age + black + marr | 
    countyfips + year,
  vcov = ~countyfips + year
)
```


## Combine Estimation Results using `etable()`

```{r}
# Reg 1
reg1 <- feols(wage ~ educ + age)

# Reg 2: Add FE
reg2 <- feols(
  wage ~ educ + age + black + marr | 
    countyfips + year
)

# Reg 3: Use twoway clustering
reg3 <- feols(
  wage ~ educ + age + black + marr | 
    countyfips + year,
  vcov = ~countyfips + year
)

# Combine the three tables
etable(reg1, reg2, reg3)
```


## Multi-Model Estimations

### Split estimation by group

```{r}
# df |> count(year)
# A tibble: 3 × 2
#    year     n
#   <dbl> <int>
# 1  1974 15992
# 2  1975 15992
# 3  1978 15992

feols(
  wage ~ educ + age + black + marr | 
    countyfips,
  vcov = ~countyfips,
  split = ~year
) |> 
  etable()
```

### Multiple dependent variables

### Stepwise regression


## Interaction Terms


## Macros

```{r}
# treat
# contr_demog
# contr_geo
# fe
```


## Presenting Better Tables for Meetings and Other Non-Publication Purposes


## Exports Table in LaTeX Format


